---
title: "Team8_Report"
author:
- familyname: Chen
  othernames: Peizhao
  address: Monash Universtidy
  email: pche0072@student.monash.edu
  correspondingauthor: true
  qualifications:  XXX
- familyname: XXXX
  othernames: Reports
  address: XXX
  qualifications: XXX
- familyname: XXX
  othernames: XXX
  address: XXX
  email: XXX
  correspondingauthor: true
  qualifications:  XXX
department: Our consultancy \newline add names &\newline add names
organization: Australian Government COVID19
bibliography: references.bib
biblio-style: authoryear-comp
linestretch: 1.5
output:
  bookdown::pdf_document2:
    template: monashreport2.tex
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    includes:
      in_header: preamble.tex
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
    toc: false
---

```{r , echo = FALSE, message = FALSE, warning = FALSE}
# Libraries
knitr::opts_chunk$set(echo=FALSE,
                      include=TRUE, 
                      messages = FALSE, 
                      warning = FALSE)

library(palmerpenguins)
library(tidyverse)
library(janitor)
library(imputeTS)
library(broom)
library(gglm)
library(patchwork)
library(flextable)
library(kableExtra)
library(datasets)
library(tidyverse)
library(datasets)
library(here)
library(readxl)
library(plotly)
library(corrplot)
library(rockchalk)
library(dplyr)
library(naniar)
```

\section*{Overall analysis from 1990 to 2013}

# Introduction

This report aims to analyze factors related to GDP growth from 1990 to 2019 in Australia.There are several parts we want to figure out by analyzing the data: overall changes in unemployment,population,GDP growth,unemployment with different education level,and unemployment by genders from 1990 to 2020.The comparison between different categories of unemployment.The factors related to the GDP growth and their relations.
The report is based on the Data of the world bank.All data of ABS presented on this website is provided under a Creative Commons Attribution 4.0 International license, it is open data and free to share and adapt for any purpose even commercially.


```{r  echo=FALSE,include=FALSE}

AUS <- read_csv(here::here("Data/AUS.csv")) %>% 
  dplyr::filter(year >= 1990 & year <= 2019) %>% 
  janitor::clean_names()

AUS1 <- read_excel(here::here("Data/A4_data.xlsx")) %>% 
  dplyr::filter(year >= 1990 & year <= 2013)%>%
  rename("Unemploy_F"=`Unemployment female`,
         "Unemploy_M"=`Unemployment male`,
         "Unemploy_T"=`Unemployment total`,
         "Advanced_edu"=`advanced education`,
         "Basic_edu"=`basic education`)
```

```{r m1,echo=FALSE,include=TRUE}

Miss_AUS1<-miss_var_summary(AUS1)

kable(Miss_AUS1, booktabs = TRUE,
  caption = 'Missing values in data')%>%
  kable_styling(c("basic",
                  fixed_thead = TRUE),
                latex_options = "HOLD_position")

```

From the given table \@ref(tab:m1)There are significant proportion of missing values in variables unemployment with advanced education and basic education.That means the research concerning these two variables should begin at 2000 .

```{r g1,fig.cap="GDP Change from 1990 to 2020" }
g1 <- AUS %>% 
  ggplot(aes(year,gdp_growth)) +
  geom_line()+
  labs(x = "Year",
       y = "percentage of GDP change")

```

From the given figure \@ref(fig:g1),only the beginning of 1990s has experienced a negative growth which was about -0.3%,and the following growth of years was fluctuating around 2.5% even after 2008 the year of financial crisis the growth is still positive.The negative growth in 1990s attribute to recession mainly resulted from Australia's efforts to address excess domestic demand,.curb speculative behaviour in commercial property markets and reduce inflation. Interest rates were increased to a very high level because the transmission of tighter monetary policy took longer than expected to put downward pressure on demand and inflation.

```{r g2,fig.cap="Population Change from 1990 to 2020"}
g2 <- AUS %>% 
  ggplot(aes(year,population)) +
  geom_line()+
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Year",
       y = "Population")


```

From the given figure \@ref(fig:g2), the Australian population has been growing steadily from 17,000,000 to over 25,000,000 in the year between 1990 to 2020.Australia has population growth rate around 1.48% averagely according to worldbank data.Migration and birth rate minus mortality rate were included in this growth rate.

```{r g3,fig.cap="Inflation Change from 1990 to 2020"}
g3 <- AUS1 %>%
  ggplot(aes(year,  `Inflation, consumer prices (annual %)`)) +
  geom_line() +
  labs(x = "Year",
       y = "Inflation rate")

```

From the given figure \@ref(fig:g3),The inflation rate was fluctuating throughout two decades.The pinnacle was in 1990,about 7% that is main attribute to the recession,While lowest point was given at 1994.

```{r echo=FALSE,include=FALSE}

AUS_edu<-AUS%>%
  select(year,
         unemployment_with_advanced_education,
         unemployment_with_basic_education)%>%
  filter(year %in%c(2000:2013))


```

```{r echo=FALSE,include=FALSE}

AUS_edu_longer<-AUS_edu%>%
  pivot_longer(cols = -c('year'),
               names_to = "Unemployment",      
               values_to = "Percent")

AUS_edu_wider<- AUS_edu_longer%>%
  pivot_wider(id_cols = Unemployment,
              names_from = year,
              values_from = Percent)%>%
   mutate(YOY_01 = paste0( 
           round((`2001`-`2000`)
                 /`2000`*100,2),"%"),
         YOY_02 = paste0( 
           round((`2002`-`2001`)
                 /`2001`*100,2),"%"),
         YOY_03 = paste0( 
           round((`2003`-`2002`)
                 /`2002`*100,2),"%"),
         YOY_04 = paste0( 
           round((`2004`-`2003`)
                 /`2003`*100,2),"%"),
         YOY_05 = paste0( 
           round((`2005`-`2004`)
                 /`2004`*100,2),"%"),
         YOY_06 = paste0( 
           round((`2006`-`2005`)
                 /`2005`*100,2),"%"),
         YOY_07 = paste0( 
           round((`2007`-`2006`)
                 /`2006`*100,2),"%"),
         YOY_08 = paste0( 
           round((`2008`-`2007`)
                 /`2007`*100,2),"%"),
         YOY_09 = paste0( 
           round((`2009`-`2008`)
                 /`2008`*100,2),"%"),
         YOY_10 = paste0( 
           round((`2010`-`2009`)
                 /`2009`*100,2),"%"),
         YOY_11 = paste0( 
           round((`2011`-`2010`)
                 /`2010`*100,2),"%"),
         YOY_12 = paste0( 
           round((`2012`-`2011`)
                 /`2011`*100,2), "%"),
         YOY_13 = paste0( 
           round((`2013`-`2012`)
                 /`2012`*100,2), "%"))%>%
  select(Unemployment,
         YOY_01:YOY_13)%>%
  rename(`2001`=YOY_01,
         `2002`=YOY_02,
         `2003`=YOY_03,
         `2004`=YOY_04,
         `2005`=YOY_05,
         `2006`=YOY_06,
         `2007`=YOY_07,
         `2008`=YOY_08,
         `2009`=YOY_09,
         `2010`=YOY_10,
         `2011`=YOY_11,
         `2012`=YOY_12,
         `2013`=YOY_13)
```

```{r educhange,echo=FALSE,include=TRUE}
AUS_edu_change_wider<-AUS_edu_wider%>%
   pivot_longer(cols = `2001`:`2013`,
               names_to = "year",
               values_to = "Percentage_of_Change")%>%
  pivot_wider(id_cols = year,
              names_from = Unemployment,
              values_from = Percentage_of_Change)%>%
  rename(unemploy_adv_edu_change=
           unemployment_with_advanced_education,
         unemploy_bas_edu_change=
           unemployment_with_basic_education)%>%
  mutate(year=as.numeric(year))

AUS_edu2<-left_join(AUS_edu,AUS_edu_change_wider,by="year")%>%
  rename(unemploy_adv_edu =
           unemployment_with_advanced_education,
         unemploy_bas_edu =
           unemployment_with_basic_education)

AUS_edu2%>%
  kable(caption ="Percent change in umemployment with different education level")%>%
   kable_styling(c("basic",
                  fixed_thead = TRUE),
                latex_options = "HOLD_position")

```

From the given table \@ref(tab:educhange),the unemployment rate of people with advanced education is much lower than people with basic education,which was changing at the rang between 4% to 2%.While the unemployment rate for people with basic education is about 10% to 8% throughout 13 years.

```{r g9,echo=FALSE,include=TRUE}

g9 <- ggplot(AUS_edu_longer,aes(x=year,y=Percent,by=Unemployment,color = factor(Unemployment)))+
  geom_line()+
  labs(color = "Unemployment by education") 
g9

```

The given figure \@ref(fig:g9) can demonstrate the change more obviously,the two lines are in completely different levels,that means the unemployment of basic education is much more higher than people with advanced education.However,they changes show similar pattern such as the downward trend from 1990 to 2006 and upward from 2007 to 2009.

```{r echo=FALSE,include=FALSE}

AUS_sex_tab<-AUS1%>%
  select(year,
         Unemploy_F,
         Unemploy_M)


```

```{r echo=FALSE,include=FALSE}

AUS_sex_longer<-AUS_sex_tab%>%
  pivot_longer(cols = -c('year'),
               names_to = "Unemployment",      
               values_to = "Percent")


AUS_sex_wider<- AUS_sex_longer%>%
  pivot_wider(id_cols = Unemployment,
              names_from = year,
              values_from = Percent)%>%
   mutate(YOY_91 = paste0( 
           round((`1991`-`1990`)
                 /`1990`*100,2),"%"),
          YOY_92 = paste0( 
           round((`1992`-`1991`)
                 /`1991`*100,2),"%"),
          YOY_93 = paste0( 
           round((`1993`-`1992`)
                 /`1992`*100,2),"%"),
          YOY_94 = paste0( 
           round((`1994`-`1993`)
                 /`1993`*100,2),"%"),
          YOY_95 = paste0( 
           round((`1995`-`1994`)
                 /`1994`*100,2),"%"),
          YOY_96 = paste0( 
           round((`1996`-`1995`)
                 /`1995`*100,2),"%"),
          YOY_97 = paste0( 
           round((`1997`-`1996`)
                 /`1996`*100,2),"%"),
          YOY_98 = paste0( 
           round((`1998`-`1997`)
                 /`1997`*100,2),"%"),
          YOY_99 = paste0( 
           round((`1999`-`1998`)
                 /`1998`*100,2),"%"),
          YOY_00 = paste0( 
           round((`2000`-`1999`)
                 /`1999`*100,2),"%"),
          YOY_01 = paste0( 
           round((`2001`-`2000`)
                 /`2000`*100,2),"%"),
         YOY_02 = paste0( 
           round((`2002`-`2001`)
                 /`2001`*100,2),"%"),
         YOY_03 = paste0( 
           round((`2003`-`2002`)
                 /`2002`*100,2),"%"),
         YOY_04 = paste0( 
           round((`2004`-`2003`)
                 /`2003`*100,2),"%"),
         YOY_05 = paste0( 
           round((`2005`-`2004`)
                 /`2004`*100,2),"%"),
         YOY_06 = paste0( 
           round((`2006`-`2005`)
                 /`2005`*100,2),"%"),
         YOY_07 = paste0( 
           round((`2007`-`2006`)
                 /`2006`*100,2),"%"),
         YOY_08 = paste0( 
           round((`2008`-`2007`)
                 /`2007`*100,2),"%"),
         YOY_09 = paste0( 
           round((`2009`-`2008`)
                 /`2008`*100,2),"%"),
         YOY_10 = paste0( 
           round((`2010`-`2009`)
                 /`2009`*100,2),"%"),
         YOY_11 = paste0( 
           round((`2011`-`2010`)
                 /`2010`*100,2),"%"),
         YOY_12 = paste0( 
           round((`2012`-`2011`)
                 /`2011`*100,2), "%"),
         YOY_13 = paste0( 
           round((`2013`-`2012`)
                 /`2012`*100,2), "%"))%>%
  select(Unemployment,
         YOY_91:YOY_13)%>%
  rename(`1991`=YOY_91,
         `1992`=YOY_92,
         `1993`=YOY_93,
         `1994`=YOY_94,
         `1995`=YOY_95,
         `1996`=YOY_96,
         `1997`=YOY_97,
         `1998`=YOY_98,
         `1999`=YOY_99,
         `2000`=YOY_00,
         `2001`=YOY_01,
         `2002`=YOY_02,
         `2003`=YOY_03,
         `2004`=YOY_04,
         `2005`=YOY_05,
         `2006`=YOY_06,
         `2007`=YOY_07,
         `2008`=YOY_08,
         `2009`=YOY_09,
         `2010`=YOY_10,
         `2011`=YOY_11,
         `2012`=YOY_12,
         `2013`=YOY_13)
```

```{r sexchange,echo=FALSE,include=TRUE}

AUS_sex_change_wider<-AUS_sex_wider%>%
   pivot_longer(cols = `1991`:`2013`,
               names_to = "year",
               values_to = "Percentage_of_Change")%>%
  pivot_wider(id_cols = year,
              names_from = Unemployment,
              values_from = Percentage_of_Change)%>%
  rename(Unemploy_F_Change=
           Unemploy_F,
         Unemploy_M_Change=
           Unemploy_M)%>%
  mutate(year=as.numeric(year))

AUS_sex2<-left_join(AUS_sex_tab,AUS_sex_change_wider,by="year")

AUS_sex2%>%
  kable(caption ="Percent change in umemployment by gender")%>%
   kable_styling(c("basic",
                  fixed_thead = TRUE),
                latex_options = "HOLD_position")

```

From the given table \@ref(tab:sexchange),the ratios of unemployment male and females show no apparent differences,which is around 4% to 10%,but in 1992 and 1993 women had experienced a high umemployment rate of over 11% ,the rate for females was soared from the beginning of 1990s.

```{r echo=FALSE,include=FALSE}

AUS_T_tab<-AUS1%>%
  select(year,
         Unemploy_T)


AUS_T_longer<-AUS_T_tab%>%
  pivot_longer(cols = -c('year'),
               names_to = "Unemployment",      
               values_to = "Percent")


AUS_T_wider<- AUS_T_longer%>%
  pivot_wider(id_cols = Unemployment,
              names_from = year,
              values_from = Percent)%>%
   mutate(YOY_91 = paste0( 
           round((`1991`-`1990`)
                 /`1990`*100,2),"%"),
          YOY_92 = paste0( 
           round((`1992`-`1991`)
                 /`1991`*100,2),"%"),
          YOY_93 = paste0( 
           round((`1993`-`1992`)
                 /`1992`*100,2),"%"),
          YOY_94 = paste0( 
           round((`1994`-`1993`)
                 /`1993`*100,2),"%"),
          YOY_95 = paste0( 
           round((`1995`-`1994`)
                 /`1994`*100,2),"%"),
          YOY_96 = paste0( 
           round((`1996`-`1995`)
                 /`1995`*100,2),"%"),
          YOY_97 = paste0( 
           round((`1997`-`1996`)
                 /`1996`*100,2),"%"),
          YOY_98 = paste0( 
           round((`1998`-`1997`)
                 /`1997`*100,2),"%"),
          YOY_99 = paste0( 
           round((`1999`-`1998`)
                 /`1998`*100,2),"%"),
          YOY_00 = paste0( 
           round((`2000`-`1999`)
                 /`1999`*100,2),"%"),
          YOY_01 = paste0( 
           round((`2001`-`2000`)
                 /`2000`*100,2),"%"),
         YOY_02 = paste0( 
           round((`2002`-`2001`)
                 /`2001`*100,2),"%"),
         YOY_03 = paste0( 
           round((`2003`-`2002`)
                 /`2002`*100,2),"%"),
         YOY_04 = paste0( 
           round((`2004`-`2003`)
                 /`2003`*100,2),"%"),
         YOY_05 = paste0( 
           round((`2005`-`2004`)
                 /`2004`*100,2),"%"),
         YOY_06 = paste0( 
           round((`2006`-`2005`)
                 /`2005`*100,2),"%"),
         YOY_07 = paste0( 
           round((`2007`-`2006`)
                 /`2006`*100,2),"%"),
         YOY_08 = paste0( 
           round((`2008`-`2007`)
                 /`2007`*100,2),"%"),
         YOY_09 = paste0( 
           round((`2009`-`2008`)
                 /`2008`*100,2),"%"),
         YOY_10 = paste0( 
           round((`2010`-`2009`)
                 /`2009`*100,2),"%"),
         YOY_11 = paste0( 
           round((`2011`-`2010`)
                 /`2010`*100,2),"%"),
         YOY_12 = paste0( 
           round((`2012`-`2011`)
                 /`2011`*100,2), "%"),
         YOY_13 = paste0( 
           round((`2013`-`2012`)
                 /`2012`*100,2), "%"))%>%
  select(Unemployment,
         YOY_91:YOY_13)%>%
  rename(`1991`=YOY_91,
         `1992`=YOY_92,
         `1993`=YOY_93,
         `1994`=YOY_94,
         `1995`=YOY_95,
         `1996`=YOY_96,
         `1997`=YOY_97,
         `1998`=YOY_98,
         `1999`=YOY_99,
         `2000`=YOY_00,
         `2001`=YOY_01,
         `2002`=YOY_02,
         `2003`=YOY_03,
         `2004`=YOY_04,
         `2005`=YOY_05,
         `2006`=YOY_06,
         `2007`=YOY_07,
         `2008`=YOY_08,
         `2009`=YOY_09,
         `2010`=YOY_10,
         `2011`=YOY_11,
         `2012`=YOY_12,
         `2013`=YOY_13)
```

```{r Tchange,echo=FALSE,include=TRUE}

AUS_T_change_wider<-AUS_T_wider%>%
   pivot_longer(cols = `1991`:`2013`,
               names_to = "year",
               values_to = "Percentage_of_Change")%>%
  pivot_wider(id_cols = year,
              names_from = Unemployment,
              values_from = Percentage_of_Change)%>%
  rename(Unemploy_T_Change=
           Unemploy_T)%>%
  mutate(year=as.numeric(year))

AUS_T2<-left_join(AUS_T_tab,AUS_T_change_wider,by="year")

AUS_T2%>%
  kable(caption ="Percent change in total umemployment")%>%
   kable_styling(c("basic",
                  fixed_thead = TRUE),
                latex_options = "HOLD_position")

```

From the given table \@ref(tab:Tchange),the total unemployment rate of Australia showed a generally downward tendency from 1990 to 2013 since in the beginning of 1990 the rate was about 10% but after 13 years the unemployment rate has decreased to 5.66% in 2013.


\section*{Country XX2 and YY2}

\section*{Country XX3 and YY3}



